Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-21 WSSSPE3/report/WSSSPE3_review.tex
Removed a comment.
Section 3 Keynote: a new paragraph.

In his keynote address, Turk recapped the course of development of WSSSPE
workshops alongside with his career from a postdoc to an academic over the past
few years. The first WSSSPE workshop was at the Supercomputing Conference (SC13)
in 2013, but he observed that the notion of sustainable scientific software drew
in an audience beyond supercomputing. In the following year, WSSSPE1.1 at SciPy
had speakers talking about how software has been sustained inside the scientific
Python community. WSSSPE2 at SC14 had breakout group discussions coming up with
actionable items, and WSSSPE2.1 at SciPy 2015 was similar. Turk noted the
different atmosphere of the surrounding large conferences, despite similar
WSSSPE participants. WSSSPE3 broke free of the Supercomputing Conference
environment this time, and in Turk's words, it spoke to the fact that scientific
software comes from many different types of inquiries, deployment, strategies
for maintenance, users; and ways of measuring the value of a piece of software.
It appeared to Turk that the supercomputing conferences generally adopt some
top-down approaches, whereas SciPy bottom-up systems; the essential messages
perceived were also often circumpolar: software getting harder in supercomputing
communities with exascale computing in mind, but software becoming better in the
SciPy groups with new tools such as Jupiter and packages for research workflow.
Admitting such comparisons are somewhat unfair generalization, Turk reminded the
audience that the different approaches bring different types of ideas to the
table, but he welcomed that WSSSPE3 was outside existing preconceptions.

%preconceptions

>>>>

In his keynote address, Turk recapped the course of development of WSSSPE
workshops alongside with his career from a postdoc to an academic over the past
few years. The first WSSSPE workshop was at the Supercomputing Conference (SC13)
in 2013, but he observed that the notion of sustainable scientific software drew
in an audience beyond supercomputing. In the following year, WSSSPE1.1 at SciPy
had speakers talking about how software has been sustained inside the scientific
Python community. WSSSPE2 at SC14 had breakout group discussions coming up with
actionable items, and WSSSPE2.1 at SciPy 2015 was similar. Turk noted the
different atmosphere of the surrounding large conferences, despite similar
WSSSPE participants.

WSSSPE3 broke free of the traditional Supercomputing Conference
environment this year, and in Turk's words, it spoke to the fact that scientific
software comes from many different types of inquiries, deployment, strategies
for maintenance, users; and ways of measuring the value of a piece of software.
It appeared to Turk that the supercomputing conferences generally adopt some
top-down approaches, whereas SciPy bottom-up systems; the essential messages
perceived were also often circumpolar: software getting harder in supercomputing
communities with exascale computing and optimization issues in mind, but software becoming better in the
SciPy groups with emerging tools such as Jupiter and productivity packages for research workflow.
Admitting such comparisons are somewhat unfair generalization, Turk reminded the
audience that the different approaches bring different types of ideas to the
table, but he welcomed that WSSSPE3 was outside existing preconceptions.
